---
title: "Bamana FASTQ Ingress Benchmark"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M %Z')`"
output:
  pdf_document:
    toc: false
params:
  tidy_csv: ""
  summary_csv: ""
  support_csv: ""
  tool_versions: ""
  fastq: ""
  bamana_bam: ""
  comparator_bam: ""
  container_image: ""
  profile: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)

tidy_runs <- read_csv(params$tidy_csv, show_col_types = FALSE)
summary_runs <- read_csv(params$summary_csv, show_col_types = FALSE)
support_matrix <- read_csv(params$support_csv, show_col_types = FALSE)
tool_versions <- read_tsv(
  params$tool_versions,
  col_names = c("tool", "version"),
  show_col_types = FALSE
)

successful_runs <- tidy_runs %>%
  filter(success) %>%
  mutate(tool = factor(tool, levels = unique(tool)))
```

## Run Summary

This report was rendered from R Markdown for the `r params$profile` profile.
The benchmark container image was `r params$container_image`.

- FASTQ input: `r params$fastq`
- Bamana BAM output: `r params$bamana_bam`
- Comparator BAM output: `r params$comparator_bam`

## Tool Versions

```{r tool-versions}
kable(tool_versions, align = c("l", "l"))
```

## Measured Runs

```{r run-table}
display_runs <- tidy_runs %>%
  transmute(
    tool,
    workflow_variant,
    status,
    semantic_equivalence,
    wall_seconds = round(wall_seconds, 3),
    max_rss_bytes,
    output_path,
    output_bytes
  )

kable(display_runs, align = "l")
```

## Wall Time

```{r wall-time-plot, fig.width=8, fig.height=4.5}
plot_data <- successful_runs %>%
  mutate(tool = factor(tool, levels = unique(tool)))

ggplot(plot_data, aes(x = tool, y = wall_seconds, fill = tool)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = sprintf("%.2fs", wall_seconds)), vjust = -0.4, size = 3.5) +
  labs(
    title = "FASTQ ingress wall time",
    x = "Tool path",
    y = "Wall seconds"
  ) +
  theme_minimal(base_size = 11)
```

## Output Size

```{r output-size-plot, fig.width=8, fig.height=4.5}
ggplot(plot_data, aes(x = tool, y = output_bytes / 1024^3, fill = tool)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = sprintf("%.2f GiB", output_bytes / 1024^3)), vjust = -0.4, size = 3.5) +
  labs(
    title = "Materialized output size",
    x = "Tool path",
    y = "Output size (GiB)"
  ) +
  theme_minimal(base_size = 11)
```

## Support Matrix

```{r support-matrix}
support_display <- support_matrix %>%
  select(
    tool,
    workflow_variant,
    scenario,
    support_status,
    attempted,
    n_runs,
    n_success,
    n_failed,
    n_unsupported
  )

kable(support_display, align = "l")
```

## Notes

The comparator path uses `fastcat` to own FASTQ.GZ ingress and pipes the
result into `samtools import` for unmapped BAM materialization. That makes the
comparison informative for ingress benchmarking while still keeping the
resulting artifact in BAM space.
