---
title: "Bamana FASTQ.GZ Enumeration Benchmark"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M %Z')`"
output:
  pdf_document:
    toc: false
params:
  tidy_csv: ""
  summary_csv: ""
  support_csv: ""
  tool_versions: ""
  fastq: ""
  bamana_output: ""
  comparator_output: ""
  bamana_output_label: ""
  comparator_output_label: ""
  container_image: ""
  profile: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)
library(jsonlite)

`%||%` <- function(lhs, rhs) {
  if (is.null(lhs) || length(lhs) == 0) {
    return(rhs)
  }
  lhs
}

format_wall_seconds <- function(value) {
  ifelse(
    is.na(value),
    "NA",
    ifelse(
      value >= 10,
      sprintf("%.2f", value),
      ifelse(value >= 1, sprintf("%.3f", value), sprintf("%.6f", value))
    )
  )
}

tidy_runs <- read_csv(params$tidy_csv, show_col_types = FALSE)
summary_runs <- read_csv(params$summary_csv, show_col_types = FALSE)
support_matrix <- read_csv(params$support_csv, show_col_types = FALSE)
tool_versions <- read_tsv(
  params$tool_versions,
  col_names = c("tool", "version"),
  show_col_types = FALSE
)

successful_runs <- tidy_runs %>%
  filter(success) %>%
  mutate(tool = factor(tool, levels = unique(tool)))

bamana_response <- fromJSON(params$bamana_output, simplifyVector = TRUE)
bamana_analysis_wall_seconds <- bamana_response$analysis_wall_seconds %||% NA_real_
```

## Run Summary

This report was rendered from R Markdown for the `r params$profile` profile.
The benchmark container image was `r params$container_image`.

- FASTQ input: `r params$fastq`
- `r params$bamana_output_label`: `r params$bamana_output`
- `r params$comparator_output_label`: `r params$comparator_output`
- Bamana internal analysis wall time: `r ifelse(is.na(bamana_analysis_wall_seconds), "NA", sprintf("%.6f s", bamana_analysis_wall_seconds))`

## Tool Versions

```{r tool-versions}
kable(tool_versions, align = c("l", "l"))
```

## Measured Runs

```{r run-table}
display_runs <- tidy_runs %>%
  transmute(
    tool,
    workflow_variant,
    status,
    semantic_equivalence,
    wall_seconds = format_wall_seconds(wall_seconds),
    max_rss_bytes,
    output_path,
    output_bytes
  )

kable(display_runs, align = "l")
```

## Wall Time

```{r wall-time-plot, fig.width=8, fig.height=4.5}
plot_data <- successful_runs %>%
  mutate(tool = factor(tool, levels = unique(tool)))

ggplot(plot_data, aes(x = tool, y = wall_seconds, fill = tool)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = sprintf("%ss", format_wall_seconds(wall_seconds))), vjust = -0.4, size = 3.5) +
  labs(
    title = "FASTQ.GZ record enumeration wall time",
    x = "Tool path",
    y = "Wall seconds"
  ) +
  theme_minimal(base_size = 11)
```

## Output Size

```{r output-size-plot, fig.width=8, fig.height=4.5}
ggplot(plot_data, aes(x = tool, y = output_bytes, fill = tool)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = sprintf("%d bytes", output_bytes)), vjust = -0.4, size = 3.5) +
  labs(
    title = "Enumeration artifact size",
    x = "Tool path",
    y = "Output size (bytes)"
  ) +
  theme_minimal(base_size = 11)
```

## Support Matrix

```{r support-matrix}
support_display <- support_matrix %>%
  select(
    tool,
    workflow_variant,
    scenario,
    support_status,
    attempted,
    n_runs,
    n_success,
    n_failed,
    n_unsupported
  )

kable(support_display, align = "l")
```

## Notes

The `fastq_gz_enumerate` profile measures how quickly Bamana can return a
stable FASTQ.GZ record count for the visible input state. When an adjacent
`FASTQ.GZI` sidecar is present, the Bamana path times indexed enumeration
rather than a full decompression pass. The comparator path remains a full
`gzip -cd` plus line-count pipeline.
